Astropy - New software standards for a growing community

### 2017-09-20 main.tex
Update on Overleaf.
first stab at abstract

\begin{abstract}

Astropy is amazing. and even more amazing than before

\end{abstract}

@@

The \texttt{astropy.coordinates} subpackage ...

- Three-tiered structure for coordinates: representation, frame, skycoord
- With differential classes, frames support velocities
- Celestial coordinates, and local coordinates (via EarthLocation + Time)
- JPL ephemerids

start with short description of the astropy approach and features (JPL ephemerids, barycentric correction, proper motions, coordinate frames) then shows the tests.

In particular, we had a discussion on problems with the definition of some coordinate system on the mailing list. Getting that discussion in here gives us a refereed paper to point to when we need to push the IAU to fix that.

>>>>

\begin{abstract}
The Astropy project supports and fosters the development of open-source Python
packages that provide commonly-needed functionality to the astronomical
community.
A key element of the project is the Astropy core package, which serves as the
foundation for more specialized projects and packages.
In this article, we provide an overview of the organization of the Astropy
project and summarize key features in the core package as of the recent major
release, version 2.0.
We then describe the project infrastructure designed to facilitate [...]
We conclude with a future outlook of planned new features and directions for the
broader Astropy ecosystem.
\end{abstract}

@@

The \texttt{astropy.coordinates} subpackage is designed to support

- Three-tiered structure for coordinates: representation, frame, skycoord
- With differential classes, frames support velocities

Accuracy and comparison of coordinate system definitions?

\subsubsection{Key features}

- Celestial coordinates, and local coordinates (via EarthLocation + Time)
- JPL ephemerids
